Data Management for LSST Special Programs

### 2024-03-01 sec_intro.tex
Update sec_intro.tex

Data from the Main Survey will be processed with standard (non-special) processing.
This processing will produce, among other data products (LSE-163), 
a contiguous sky footprint that covers at 
least $\sim$18000 deg$^2$ (with $\gtrsim$800 visits per field in WFD regions), 
and is expected to be accomplished with 85--90\% of the observing time.
This contiguous all-sky "deep coadd" may have region-dependent processing parameters and inputs
(e.g., different calibration parameters or deblending algorithms for crowded fields)
and will be of variable depth, as most special regions recieve fewer visits.

@@

\subsection{Standard (non-special) processing}

>>>>

Data from the Main Survey will be processed with standard (non-special) processing (Section~\ref{ssec:intro_stdproc}).
This processing will produce, among other data products (LSE-163), 
a contiguous sky footprint that covers at 
least $\sim$18000 deg$^2$ (with $\gtrsim$800 visits per field in WFD regions), 
and is expected to be accomplished with 85--90\% of the observing time.
This contiguous all-sky "deep coadd" may have region-dependent processing parameters and inputs
(e.g., different calibration parameters or deblending algorithms for crowded fields)
and will be of variable depth, as most special regions recieve fewer visits.

@@

Examples of Special Processing include the processing
of images with non-standard exposure times, images obtained
during twilight, or nightly stacking and differencing
of images in deep drilling fields.
See \Section~\ref{ssec:proc_special} for more detailed examples of Special Processing.

\subsection{Standard (non-special) processing}\label{ssec:intro_stdproc}
